%
% don't hide one's light under a bushel
\message{-*- Harry Newton is the best man -*-}
%                                                                                                                        
\hsize=140mm
\vsize=227mm
% remove default TeX margin
\advance\voffset by -1truein
\advance\hoffset by -1truein
\advance\voffset by 35mm
\advance\hoffset by 35mm
%
\baselineskip=16pt
\parindent=0pt
\parskip=12pt
%
\font\headfont=cmcsc10 scaled \magstep1
\def\heading#1{\centerline{\headfont#1}}
\font\notefont=cmti10 scaled \magstep1
\font\bodyfont=cmr10 scaled \magstep1
\bodyfont

\heading{Introduction}

{\notefont A locked room full of people and a microphone --- how I've
dreamed of this moment.}

Thankyou. Please rest assured I won't be swearing tonight --- James
may be after I've finished though. However, I won't be speaking for
too long for health reasons --- he's threatened to strangle me if I
say too much !

Ladies and Gentlemen --- for those of you who don't know me, I'm Harry
and I used to work with James --- used to work at the same company ---
well --- I used to hang arond the same office as he did.

I'm obviously the best man --- well I hope it's obvious. If anyone
wants to know why I'm the best man --- please see me afterwards ---
when I'll be more than happy to give a demonstration. No really ---
anyone.

Before I undertake my chief responsibility --- the ritual
assassination of James's character --- I should like to thank him on
behalf of the bridesmaids Ee-fah, Gemma, Sophie, and Jessica for his
kind words about them, and echo them myself.

I'd like to thank James for choosing me to be his best man --- I feel
profoundly humbled and honoured as a result --- and profoundly scared
and terrified that he's built anticipation of my speech to a level
that I can't possibly sustain. However --- it's not my responsibility
--- this speech contains little or no original matter --- so if
anyone's offended by that --- they should take the matter up with
Google Incorporated who have provided most of the material.

I knew James was in love when he changed into a happy, smiling,
carefree person --- rather than the miserable and bitter man I'd
always known.

And as soon as I met Maeve --- who looks absolutely stunning today ---
I knew why James had fallen in love with her. She is a truly
beautiful, sweet, loving, caring, and funny woman.

\bigskip\heading{James}

It's not often you have an opportunity to stand-up in front of a large
crowd, and compliment your best friend, pointing out his many
outstanding qualities and achievements, highlighting his successes and
praising his many virtues.

Tonight's really not going to be any different !

Of course, having participated in many of James's escapades over the
years I'm not going to reveal too much --- in a desperate attempt to
cling on to any remaining credibility I still have. And some of the
incidents are still sub judice.

James was born on Wednesday the fifth of May eighteen seventy ---
nineteen seventy-one. The chart number one was Joy to the World.

Even from an early age he displayed a keen interest and curiosity
about the world. Taken shopping he was left just for a few minutes in
his pram --- which had all the accoutrements of childhood --- blanket,
rattle --- and with hindsight perhaps unwisely --- a tin of white
emulsion --- the lid of which he quickly managed to prise off --- and
was soon merrily spreading the paint all over the pram --- all over
himself --- before starting to ladle the stuff down his throat. I am
absolutely sure this is why he's such a whiter than white character.

He carried on with this individual approach when he went to the
University of Manchester excelling at computation and software
engineering --- although he was actually studying physics at the
time. This did set up him though --- and a few years ago he landed a
job at a small internet search company --- goggle --- giggle ---
something like that. Don't use them myself --- but I know exactly
where to get my --- internet material --- from.

He's sometimes a little forgetful --- no more than most of us ---
though I am reminded of the time that we went rock climbing together
--- and he forgot the rope. Personally I enjoyed the drive through
Derbyshire to the crag --- the driving round Derbyshire to get another
rope --- and the drive back to the crag --- and then the immediate
drive back home through the twilight.

He's a keen photographer --- I mean really keen. When I was travelling
in South East Asia, James flew over to join me for a while. When he
arrived at the airport he came with a large suitcase --- and I thought
that's James all over --- well prepared thinking ahead --- I wonder
what's packed --- mosquito net --- no --- first aid kit --- no ---
guidebooks --- no --- full change of clothes --- no. In fact the
suitcase was full of cameras --- seven in all --- flash guns, lenses
--- the only thing that wasn't camera was a teeshirt.

He's a good business man --- in Cambodia he displayed formidable
negotiation skills --- bartering with a guidebook seller he was able
to beat them up from five dollars to twenty dollars in a matter of
minutes. We were both surprizingly popular with the street merchants
afterwards.

He loves music --- he loves what he calls music --- especially sharing
it with his flat mates.

I asked a mutual colleague how he would describe James.

"Vell --- always still on feet at end of party. This means either he
is cheat, or chronic alcoholic."

(That's right --- the colleague is Welsh).

\bigskip
So --- that's the character assassination bit over. In fact James does
have one or two good things about him. He {\notefont is} a very good
photographer --- and I'd urge you to have a look at some of the
stunning pictures he's taken. He's great to talk to --- a witty and
pleasant conversationalist --- I really miss sitting in a pub with him
and talking. He's a very loyal and very good friend to a lot of people
--- he's sedulous in maintaining his friendships --- and always
solicitous of his friend's well being --- and he's something that is
increasingly rare these days --- an absolute gentleman.

\bigskip\heading{Close}

Well --- it gives me very great pleasure - and quite a bit of relief -
to propose a massive toast to two of the most beautiful, lovely, and
wonderful people I've ever had the fortune to have in my life.

So if I could invite you all to stand, and raise your glasses to the
new Mr and Mrs Youngman --- to their future --- our good fortune in
sharing in it --- and everyone having a blast in the celebration of
this wonderful day ---

To James and Maeve !

\bye

% Local variables:
% compile-command: "pdftex speech"
% End:
